XOR-Some Prolific Pilot 1

### 2021-03-27 analysis/xor-some-prolific-pilot1.Rmd
added correlation plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

Plot mean ratings (across all 10 participants) for each vignette (with its respective condition indicated in the facet title, in the order relevance/competence/prior), in each condition. For relevance and competence, the color indicates whether it was presented without the utterance or with. 
```{r, fig.width=10, fig.height=7}
bar.width = 0.8
d_critical %>% 
  mutate(title = paste(title, exp_condition, sep = "_")) %>%
  filter(block == class_condition | block == "xor" | block == "some") %>%
  group_by(block, title, w_utterance, main_type) %>%
  summarize(mean_rating = mean(response)) %>% 
  ggplot(., aes(x = block, y = mean_rating, fill = w_utterance)) +
  geom_col(alpha = 0.7, width = bar.width, position = position_dodge(width = bar.width)) +
  #geom_point(size = 2, alpha = 0.5, position = position_jitter(width = 0.1)) +
  facet_wrap(main_type~title, ncol = 4) +
  theme(axis.text.x = element_text(angle = 45)) +
  ggtitle("By-item by-question mean ratings")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings = FALSE, message = FALSE)
```

@@

Create more extensive condition labels, including information about whether a rating was produced with or without the utterance given.

``` {r}
# extending 'conditions' labels to include wheter the utterance was present or not
d_critical <- d_critical %>% 
  mutate(block_extended = ifelse(
    !w_utterance, 
    block, 
    ifelse(block %in% c("some", "xor"), "target", str_c(block, "_wUtt", ""))
  ))
```

Plot mean ratings (across all 10 participants) for each vignette (with its respective condition indicated in the facet title, in the order relevance/competence/prior), in each condition. For relevance and competence, the color indicates whether it was presented without the utterance or with. 
```{r, fig.width=10, fig.height=7}
bar.width = 0.8
d_critical %>% 
  mutate(title = paste(title, exp_condition, sep = "_")) %>%
  filter(block == class_condition | block == "xor" | block == "some") %>%
  group_by(block_extended, title, w_utterance, main_type) %>%
  summarize(mean_rating = mean(response)) %>% 
  ggplot(., aes(x = block_extended, y = mean_rating, fill = w_utterance)) +
  geom_col(alpha = 0.7, width = bar.width, position = position_dodge(width = bar.width)) +
  #geom_point(size = 2, alpha = 0.5, position = position_jitter(width = 0.1)) +
  facet_wrap(main_type~title, ncol = 4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("By-item by-question mean ratings")
```

``` {r}
# make a versatile wide representation of the critical data
d_critical_wide <- d_critical %>% 
  select(submission_id, title, main_type, block_extended, response) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response, 
    values_fn = mean # getting means for double prior measurement in "xor"
  )

# correlation plot for "some"
GGally::ggpairs(
  filter(d_critical_wide, main_type == "some") %>%  
    select(prior:ncol(d_critical_wide))
)

# correlation plot for "or"
GGally::ggpairs(
  filter(d_critical_wide, main_type == "xor") %>%  
    select(prior:ncol(d_critical_wide))
  )
```
